\documentclass{article}

\usepackage{amsmath}
\usepackage{graphicx}

\begin{document}

\section{Roman Numeral Worksheet}

This worksheet contains 20 questions about Roman numerals. Each question has four answer choices.

\begin{enumerate}

\item What is the Roman numeral for 1?

(a) I
(b) II
(c) III
(d) IV

\item What is the Roman numeral for 2?

(a) II
(b) III
(c) IV
(d) V

\item What is the Roman numeral for 3?

(a) III
(b) IV
(c) V
(d) VI

\item What is the Roman numeral for 4?

(a) IV
(b) V
(c) VI
(d) VII

\item What is the Roman numeral for 5?

(a) V
(b) VI
(c) VII
(d) VIII

\item What is the Roman numeral for 6?

(a) VI
(b) VII
(c) VIII
(d) IX

\item What is the Roman numeral for 7?

(a) VII
(b) VIII
(c) IX
(d) X

\item What is the Roman numeral for 8?

(a) VIII
(b) IX
(c) X
(d) XI

\item What is the Roman numeral for 9?

(a) IX
(b) X
(c) XI
(d) XII

\item What is the Roman numeral for 10?

(a) X
(b) XI
(c) XII
(d) XIII

\item What is the Roman numeral for 11?

(a) XI
(b) XII
(c) XIII
(d) XIV

\item What is the Roman numeral for 12?

(a) XII
(b) XIII
(c) XIV
(d) XV

\item What is the Roman numeral for 13?

(a) XIII
(b) XIV
(c) XV
(d) XVI

\item What is the Roman numeral for 14?

(a) XIV
(b) XV
(c) XVI
(d) XVII

\item What is the Roman numeral for 15?

(a) XV
(b) XVI
(c) XVII
(d) XVIII

\item What is the Roman numeral for 16?

(a) XVI
(b) XVII
(c) XVIII
(d) XIX

\item What is the Roman numeral for 17?

(a) XVII
(b) XVIII
(c) XIX
(d) XX

\item What is the Roman numeral for 18?

(a) XVIII
(b) XIX
(c) XX
(d) XXI

\item What is the Roman numeral for 19?

(a) XIX
(b) XX
(c) XXI
(d) XXII

\end{enumerate}

\end{document}
